---
title: "PAART Analysis - Simulated Data"
output: html_notebook
---

Package "gnm" is used to carry out sum of exponential fits; package "msm" is used to estimate standard error for responses and off rates using Delta method.
```{r, warning = F}
library(readxl)
library(gnm)
library(plyr)
library(xlsx)
library(grid)
library(gridBase)
library(gridExtra)
library(msm)
suppressPackageStartupMessages(library(R.utils))
```

Import compiled table containing raw data points and sample identifiers, example file formats are .xlsx, .csv and and .rdata 
```{r}
alldata = read_xlsx("Simulated PAART Data v2.xlsx", sheet = 1)
```

Import sample info sheet containing the sample identifiers, the fitting window for each curve, and whether to include a specific curve for fitting.
```{r}
samplewindow = read_xlsx("Simulated PAART Data windows v2.xlsx", sheet = 1)
samplewindow = samplewindow[which(samplewindow$Include == "Y"),]
```

If there are duplicate rows in the info sheet, this line helps delete them.
```{r}
uniquesample = unique(samplewindow)
```

Parameter intialization options for responses:
1. No initialization
2. Zero
3. The log of 100%, 1/2 or 1/3 of the highest response, depending on the number of components (recommended)
4. The log of the highest response, regardless of number of components
5. 100%, 1/2 or 1/3 of the highest response, depending on the number of components (not recommended)
6. The highest response, regardless of number of components (not recommended)

```{r}
startnum = 1    # The starting row number in info sheet (uniquesample) to be included in fitting
endnum = nrow(uniquesample)     # The ending row number in info sheet (uniquesample) to be included in fitting
plotstart = 300     # The starting time of dissociation
plotend = 900     # The ending time of dissociation
normallist = 1:nrow(uniquesample)     # A list, could be the same as or a subset of the included rows, further excluding undesirable curves
initchoice = 3    # The choice of parameter initialization
rinfon = "N"    # Y or N, whether to include R_infinity in fitting
thinfreq = 5    # Thinning frequency, for example, 5 means taking 1 out of every 5 data points. 1 for no thinning
tmoutlimit = 1    # The maximum allowed time in seconds for each individual fitting step; if fitting fails to converge in the allowed time, the code will skip over this step; because the best fit will be selected out of repeated attemps of the same fitting type, this number affects the total fitting time.
```

Define the page titles to be used during PDF export.
```{r}
pagetitles = array(NA, dim = c(endnum-startnum+1))
for (j in startnum:endnum)
{
  pagetitles[j] = paste(uniquesample$Participant.ID[j],"_",uniquesample$Visit[j])
}
```

Execute as is.
```{r}
comp1fitstat = array(NA, dim = c(endnum-startnum+1,5))
comp2fitstat = array(NA, dim = c(endnum-startnum+1,9))
comp3fitstat = array(NA, dim = c(endnum-startnum+1,13))
comp1fitpass = array(NA, dim = c(endnum-startnum+1))
comp2fitpass = array(NA, dim = c(endnum-startnum+1))
comp3fitpass = array(NA, dim = c(endnum-startnum+1))
```

Execute as is.
```{r}
rawfull = list()
rawpoint = list()
rawpointplot = list()
comp1fits = list()
comp2fits = list()
comp3fits = list()
```

Curve fitting
```{r, warning=FALSE}
for (j in normallist)
{
  # Use the compelete combination of identifiers (in this case participant.ID and Visit) to extract data points for individual curves
  
  sampledata = alldata[which(alldata$Participant.ID==uniquesample$Participant.ID[j] & alldata$Visit==uniquesample$Visit[j]),][,c("Time","Response")]
  colnames(sampledata) = c("Time1","Response")
  sampledata = sampledata[order(sampledata$Time1),]
  
  rawfull[[j]] = sampledata
  
  # Use the fitting window defined in the info sheet to truncate dissociation data; data thinning
  
  sampledata1 = sampledata[which(sampledata$Time1>=as.numeric(uniquesample$Start[j])&sampledata$Time1<as.numeric(uniquesample$Stop[j])),]
  xfull = as.vector(t(t(sampledata1[,1]))) - as.vector(t(t(sampledata1[1,1])))
  yfull = as.vector(t(t(sampledata1[,2])))
  x = if(thinfreq==1){xfull}else{xfull[seq(1, length(xfull), thinfreq)]}
  y = if(thinfreq==1){yfull}else{yfull[seq(1, length(yfull), thinfreq)]}
  
  rawpoint[[j]] = cbind(x,y)
  
  # Find maximum response, for parameter initialization during fitting
  
  ymaxtemp = max(y)
  lgymaxtemp = if(ymaxtemp<1E-7){-7}else{log(ymaxtemp)}
  lgymaxtemphf = if(ymaxtemp<1E-7){-7}else{log(ymaxtemp/2)}
  lgymaxtempthd = if(ymaxtemp<1E-7){-7}else{log(ymaxtemp/3)}
  
  # Extract dissociation curve without data thinning for plotting purpose
  
  sampledata2 = sampledata[which(sampledata$Time1>=as.numeric(uniquesample$Start[j])&sampledata$Time1<plotend),]
  x1full = as.vector(t(t(sampledata2[,1]))) - as.vector(t(t(sampledata2[1,1])))
  y1full = as.vector(t(t(sampledata2[,2])))
  x1 = if(thinfreq==1){x1full}else{x1full[seq(1, length(x1full), thinfreq)]}
  y1 = if(thinfreq==1){y1full}else{y1full[seq(1, length(y1full), thinfreq)]}
  
  rawpointplot[[j]] = cbind(x1,y1)
  
  # Fitting when R_infinity is on
  
  if(rinfon == "Y")
  {
    
    # Fitting of 2 off rate components
    
    saved.fits2 = list()
  for (i in 1:20)
    {
    if(initchoice==1){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, NA, -0.0005, NA, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, 0, -0.0005, 0, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, lgymaxtemphf, -0.0005, lgymaxtemphf, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, lgymaxtemp, -0.0005, lgymaxtemp, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, ymaxtemp/2, -0.0005, ymaxtemp/2, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, ymaxtemp, -0.0005, ymaxtemp, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
  if(length(saved.fits2)!=0)
  {
  for (i in 21:100)
    {
    if(initchoice==1){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, NA, -0.0005, NA, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, 0, -0.0005, 0, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, lgymaxtemphf, -0.0005, lgymaxtemphf, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, lgymaxtemp, -0.0005, lgymaxtemp, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, ymaxtemp/2, -0.0005, ymaxtemp/2, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2), start = c(0, ymaxtemp, -0.0005, ymaxtemp, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
  }
    
    # Fitting of 3 off rate components
    
  saved.fits4 = list()
  for (i in 1:20)
    {
    if(initchoice==1){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, NA, -0.0005, NA, -0.005, NA, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, 0, -0.0005, 0, -0.005, 0, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, lgymaxtempthd, -0.0005, lgymaxtempthd, -0.005, lgymaxtempthd, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, lgymaxtemp, -0.0005, lgymaxtemp, -0.005, lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, ymaxtemp/3, -0.0005, ymaxtemp/3, -0.005, ymaxtemp/3, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, ymaxtemp, -0.0005, ymaxtemp, -0.005, ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
  if(length(saved.fits4)!=0)
  {
    for (i in 21:100)
    {
    if(initchoice==1){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, NA, -0.0005, NA, -0.005, NA, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, 0, -0.0005, 0, -0.005, 0, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, lgymaxtempthd, -0.0005, lgymaxtempthd, -0.005, lgymaxtempthd, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, lgymaxtemp, -0.0005, lgymaxtemp, -0.005, lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, ymaxtemp/3, -0.0005, ymaxtemp/3, -0.005, ymaxtemp/3, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, ymaxtemp, -0.0005, ymaxtemp, -0.005, ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
    while (length(saved.fits4)<100)
    {
      for (i in 100:100)
      {
    if(initchoice==1){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, NA, -0.0005, NA, -0.005, NA, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, 0, -0.0005, 0, -0.005, 0, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, lgymaxtempthd, -0.0005, lgymaxtempthd, -0.005, lgymaxtempthd, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, lgymaxtemp, -0.0005, lgymaxtemp, -0.005, lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, ymaxtemp/3, -0.0005, ymaxtemp/3, -0.005, ymaxtemp/3, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3), start = c(0, ymaxtemp, -0.0005, ymaxtemp, -0.005, ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
      }
    }
  }  
  
  # Fitting of 1 off rate component
  
  saved.fits5 = list()
  for (i in 1:100)
    {
    if(initchoice==1){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1), start = c(0, NA, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1), start = c(0, 0, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1), start = c(0, lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1), start = c(0, lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1), start = c(0, ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1), start = c(0, ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
  
  fits2aic = array(NA,dim = c(100,1))
  fits4aic = array(NA,dim = c(100,1))
  fits5aic = array(NA,dim = c(100,1))
  
  # Find fits with the lowest AIC and record the parameter values and standard deviation
  
  # Record results for 2 component fit
  
  if(length(saved.fits2)==0)
  {
    comp2fits[[j]] = y
    comp2fitstat[j,] = c(0,0,0.0000001,0,0,0,0.0000001,0,0)
    fits2allpara = as.data.frame(t(rbind(rep(0,100),rep(0,100),rep(0.0000001,100),rep(0,100),rep(0.0000001,100))))
    colnames(fits2allpara) = c("AIC","RU1","kd1","RU2","kd2")
    comp2fitpass[j] = "N"
  }
  else
  {
  for (i in 1:100)
  { 
    if(capture.output(saved.fits2[[i]]) == "NULL"){fits2aic[i]  = 0}else{fits2aic[i] = AIC(saved.fits2[[i]])[1]}
  }
  
  decayrt2 = array(NA,dim = c(4,100))
  for (i in 1:100)
  {
    if(capture.output(saved.fits2[[i]]) != "NULL")
    {
      decayrt2[[1,i]] = signif(exp(as.numeric(saved.fits2[[i]]$coefficients[2])),3)
      decayrt2[[2,i]] = signif(-as.numeric(saved.fits2[[i]]$coefficients[3]),3)
      decayrt2[[3,i]] = signif(exp(as.numeric(saved.fits2[[i]]$coefficients[4])),3)
      decayrt2[[4,i]] = signif(-as.numeric(saved.fits2[[i]]$coefficients[5]),3)
    }
  }
  
  fits2allpara = cbind(fits2aic,t(decayrt2))
  fits2allpara = as.data.frame(fits2allpara)
  colnames(fits2allpara) = c("AIC","RU1","kd1","RU2","kd2")
  fits2allpara = fits2allpara[order(fits2allpara$AIC),]
  
  comp2fits[[j]] = saved.fits2[[as.numeric(rownames(fits2allpara)[1])]]
  comp2temp = as.numeric(fits2allpara[1,])
  comp2temp2 = as.data.frame(split(comp2temp[-1], rep(1:2)))
  comp2sdtemp = signif(deltamethod(c(~x1,~exp(x2),~-x3,~exp(x4),~-x5), coefficients(comp2fits[[j]]), vcov(comp2fits[[j]])),3)
  comp2sdtemp2 = as.data.frame(split(comp2sdtemp[-1], rep(1:2)))
  comp2sdtemp3 = cbind(comp2temp2,comp2sdtemp2)
  comp2temp3 = comp2sdtemp3[order(abs(comp2sdtemp3[,2]), decreasing = F),]
  comp2temp4 = as.numeric(unlist(t(comp2temp3)))
  comp2temp5 = c(comp2temp[1],comp2temp4)
  comp2fitstat[j,] = comp2temp5
  comp2fitpass[j] = "Y"
  }
  
  # Record results for 3 component fit
  
  if(length(saved.fits4)==0)
  {
    comp3fits[[j]] = y
    comp3fitstat[j,] = c(0,0,0.0000001,0,0,0,0.0000001,0,0,0,0.0000001,0,0)
    fits4allpara = as.data.frame(t(rbind(rep(0,100),rep(0,100),rep(0.0000001,100),rep(0,100),rep(0.0000001,100),rep(0,100),rep(0.0000001,100))))
    colnames(fits4allpara) = c("AIC","RU1","kd1","RU2","kd2","RU3","kd3")
    comp3fitpass[j] = "N"
  }
  else
  {
  for (i in 1:100)
  { 
    if(capture.output(saved.fits4[[i]]) == "NULL"){fits4aic[i]  = 0}else{fits4aic[i] = AIC(saved.fits4[[i]])[1]}
  }
  
  decayrt4 = array(NA,dim = c(6,100))
  for (i in 1:100)
  {
    if(capture.output(saved.fits4[[i]]) != "NULL")
    {
      decayrt4[[1,i]] = signif(exp(as.numeric(saved.fits4[[i]]$coefficients[2])),3)
      decayrt4[[2,i]] = signif(-as.numeric(saved.fits4[[i]]$coefficients[3]),3)
      decayrt4[[3,i]] = signif(exp(as.numeric(saved.fits4[[i]]$coefficients[4])),3)
      decayrt4[[4,i]] = signif(-as.numeric(saved.fits4[[i]]$coefficients[5]),3)
      decayrt4[[5,i]] = signif(exp(as.numeric(saved.fits4[[i]]$coefficients[6])),3)
      decayrt4[[6,i]] = signif(-as.numeric(saved.fits4[[i]]$coefficients[7]),3)
    }
  }
  
  fits4allpara = cbind(fits4aic,t(decayrt4))
  fits4allpara = as.data.frame(fits4allpara)
  colnames(fits4allpara) = c("AIC","RU1","kd1","RU2","kd2","RU3","kd3")
  fits4allpara = fits4allpara[order(fits4allpara$AIC),]
 
  comp3fits[[j]] = saved.fits4[[as.numeric(rownames(fits4allpara)[1])]]
  comp3temp = as.numeric(fits4allpara[1,])
  comp3temp2 = as.data.frame(split(comp3temp[-1], rep(1:2)))
  comp3sdtemp = signif(deltamethod(c(~x1,~exp(x2),~-x3,~exp(x4),~-x5,~exp(x6),~-x7), coefficients(comp3fits[[j]]), vcov(comp3fits[[j]])),3)
  comp3sdtemp2 = as.data.frame(split(comp3sdtemp[-1], rep(1:2)))
  comp3sdtemp3 = cbind(comp3temp2,comp3sdtemp2)
  comp3temp3 = comp3sdtemp3[order(abs(comp3sdtemp3[,2]), decreasing = F),]
  comp3temp4 = as.numeric(unlist(t(comp3temp3)))
  comp3temp5 = c(comp3temp[1],comp3temp4)
  comp3fitstat[j,] = comp3temp5
  comp3fitpass[j] = "Y"
  }
  
  # Record results for 1 component fit
  
  if(length(saved.fits5)==0)
  {
    comp1fits[[j]] = y
    comp1fitstat[j,] = c(0,0,0.0000001,0,0)
    fits5allpara = as.data.frame(t(rbind(rep(0,100),rep(0,100),rep(0.0000001,100))))
    colnames(fits5allpara) = c("AIC","RU1","kd1")
    comp1fitpass[j] = "N"
  }
  else
  {
  for (i in 1:100)
  {
    if(capture.output(saved.fits5[[i]]) == "NULL"){fits5aic[i]  = 0}else{fits5aic[i] = AIC(saved.fits5[[i]])[1]}
  }
  
  decayrt5 = array(NA,dim = c(2,100))
  for (i in 1:100)
  {
    if(capture.output(saved.fits5[[i]]) != "NULL")
    {
      decayrt5[[1,i]] = signif(exp(as.numeric(saved.fits5[[i]]$coefficients[2])),3)
      decayrt5[[2,i]] = signif(-as.numeric(saved.fits5[[i]]$coefficients[3]),3)
    }
  }
  
  fits5allpara = cbind(fits5aic,t(decayrt5))
  fits5allpara = as.data.frame(fits5allpara)
  colnames(fits5allpara) = c("AIC","RU1","kd1")
  fits5allpara = fits5allpara[order(fits5allpara$AIC),]
  
  comp1fits[[j]] = saved.fits5[[as.numeric(rownames(fits5allpara)[1])]]
  comp1sdtemp = signif(deltamethod(c(~x1,~exp(x2),~-x3), coefficients(comp1fits[[j]]), vcov(comp1fits[[j]])),3)
  comp1fitstat[j,] = c(as.numeric(fits5allpara[1,]),comp1sdtemp[-1])
  comp1fitpass[j] = "Y"
  }
  }
  
  # Fitting when R_infinity is off
  
  else
  {
    
  # Fitting of 2 off rate components
    
  saved.fits2 = list()
  for (i in 1:20)
    {
    if(initchoice==1){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(NA, -0.0005, NA, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(0, -0.0005, 0, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(lgymaxtemphf, -0.0005, lgymaxtemphf, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(lgymaxtemp, -0.0005, lgymaxtemp, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(ymaxtemp/2, -0.0005, ymaxtemp/2, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(ymaxtemp, -0.0005, ymaxtemp, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
  if(length(saved.fits2)!=0)
  {
    for (i in 21:100)
    {
    if(initchoice==1){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(NA, -0.0005, NA, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(0, -0.0005, 0, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(lgymaxtemphf, -0.0005, lgymaxtemphf, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(lgymaxtemp, -0.0005, lgymaxtemp, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(ymaxtemp/2, -0.0005, ymaxtemp/2, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits2[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 2)+0, start = c(ymaxtemp, -0.0005, ymaxtemp, -0.005), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
  }
  
  # Fitting of 3 off rate components
  
  saved.fits4 = list()
  for (i in 1:20)
    {
    if(initchoice==1){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(NA, -0.0005, NA, -0.005, NA, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(0, -0.0005, 0, -0.005, 0, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(lgymaxtempthd, -0.0005, lgymaxtempthd, -0.005, lgymaxtempthd, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(lgymaxtemp, -0.0005, lgymaxtemp, -0.005, lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(ymaxtemp/3, -0.0005, ymaxtemp/3, -0.005, ymaxtemp/3, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(ymaxtemp, -0.0005, ymaxtemp, -0.005, ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
  if(length(saved.fits4)!=0)
  {
    for (i in 21:100)
    {
    if(initchoice==1){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(NA, -0.0005, NA, -0.005, NA, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(0, -0.0005, 0, -0.005, 0, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(lgymaxtempthd, -0.0005, lgymaxtempthd, -0.005, lgymaxtempthd, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(lgymaxtemp, -0.0005, lgymaxtemp, -0.005, lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(ymaxtemp/3, -0.0005, ymaxtemp/3, -0.005, ymaxtemp/3, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(ymaxtemp, -0.0005, ymaxtemp, -0.005, ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
    while (length(saved.fits4)<100)
    {
      for (i in 100:100)
      {
    if(initchoice==1){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(NA, -0.0005, NA, -0.005, NA, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(0, -0.0005, 0, -0.005, 0, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(lgymaxtempthd, -0.0005, lgymaxtempthd, -0.005, lgymaxtempthd, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(lgymaxtemp, -0.0005, lgymaxtemp, -0.005, lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(ymaxtemp/3, -0.0005, ymaxtemp/3, -0.005, ymaxtemp/3, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits4[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 3)+0, start = c(ymaxtemp, -0.0005, ymaxtemp, -0.005, ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
      }
    }
  }
  
  # Fitting of 1 off rate component
  
  saved.fits5 = list()
  for (i in 1:100)
    {
    if(initchoice==1){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1)+0, start = c(NA, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==2){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1)+0, start = c(0, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==3){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1)+0, start = c(lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==4){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1)+0, start = c(lgymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else if(initchoice==5){saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1)+0, start = c(ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    else{saved.fits5[[i]] = withTimeout(gnm(y ~ instances(Exp(1 + x), 1)+0, start = c(ymaxtemp, -0.05), verbose = FALSE, iterMax = 20000), timeout=tmoutlimit, onTimeout = "silent")}
    }
  
  fits2aic = array(NA,dim = c(100,1))
  fits4aic = array(NA,dim = c(100,1))
  fits5aic = array(NA,dim = c(100,1))
  
  # Find fits with the lowest AIC and record the parameter values and standard deviation
  
  # Record results for 2 component fit
  
  if(length(saved.fits2)==0)
  {
    comp2fits[[j]] = y
    comp2fitstat[j,] = c(0,0,0.0000001,0,0,0,0.0000001,0,0)
    fits2allpara = as.data.frame(t(rbind(rep(0,100),rep(0,100),rep(0.0000001,100),rep(0,100),rep(0.0000001,100))))
    colnames(fits2allpara) = c("AIC","RU1","kd1","RU2","kd2")
    comp2fitpass[j] = "N"
  }
  else
  {
  for (i in 1:100)
  { 
    if(capture.output(saved.fits2[[i]]) == "NULL"){fits2aic[i]  = 0}else{fits2aic[i] = AIC(saved.fits2[[i]])[1]}
  }
  
  decayrt2 = array(NA,dim = c(4,100))
  for (i in 1:100)
  {
    if(capture.output(saved.fits2[[i]]) != "NULL")
    {
      decayrt2[[1,i]] = signif(exp(as.numeric(saved.fits2[[i]]$coefficients[1])),3)
      decayrt2[[2,i]] = signif(-as.numeric(saved.fits2[[i]]$coefficients[2]),3)
      decayrt2[[3,i]] = signif(exp(as.numeric(saved.fits2[[i]]$coefficients[3])),3)
      decayrt2[[4,i]] = signif(-as.numeric(saved.fits2[[i]]$coefficients[4]),3)
    }
  }
  
  fits2allpara = cbind(fits2aic,t(decayrt2))
  fits2allpara = as.data.frame(fits2allpara)
  colnames(fits2allpara) = c("AIC","RU1","kd1","RU2","kd2")
  fits2allpara = fits2allpara[order(fits2allpara$AIC),]
  
  comp2fits[[j]] = saved.fits2[[as.numeric(rownames(fits2allpara)[1])]]
  comp2temp = as.numeric(fits2allpara[1,])
  comp2temp2 = as.data.frame(split(comp2temp[-1], rep(1:2)))
  comp2sdtemp = signif(deltamethod(c(~exp(x1),~-x2,~exp(x3),~-x4), coefficients(comp2fits[[j]]), vcov(comp2fits[[j]])),3)
  comp2sdtemp2 = as.data.frame(split(comp2sdtemp, rep(1:2)))
  comp2sdtemp3 = cbind(comp2temp2,comp2sdtemp2)
  comp2temp3 = comp2sdtemp3[order(abs(comp2sdtemp3[,2]), decreasing = F),]
  comp2temp4 = as.numeric(unlist(t(comp2temp3)))
  comp2temp5 = c(comp2temp[1],comp2temp4)
  comp2fitstat[j,] = comp2temp5
  comp2fitpass[j] = "Y"
  }
  
  # Record results for 3 component fit

  
  if(length(saved.fits4)==0)
  {
    comp3fits[[j]] = y
    comp3fitstat[j,] = c(0,0,0.0000001,0,0,0,0.0000001,0,0,0,0.0000001,0,0)
    fits4allpara = as.data.frame(t(rbind(rep(0,100),rep(0,100),rep(0.0000001,100),rep(0,100),rep(0.0000001,100),rep(0,100),rep(0.0000001,100))))
    colnames(fits4allpara) = c("AIC","RU1","kd1","RU2","kd2","RU3","kd3")
    comp3fitpass[j] = "N"
  }
  else
  {
  for (i in 1:100)
  { 
    if(capture.output(saved.fits4[[i]]) == "NULL"){fits4aic[i]  = 0}else{fits4aic[i] = AIC(saved.fits4[[i]])[1]}
  }
  
  decayrt4 = array(NA,dim = c(6,100))
  for (i in 1:100)
  {
    if(capture.output(saved.fits4[[i]]) != "NULL")
    {
      decayrt4[[1,i]] = signif(exp(as.numeric(saved.fits4[[i]]$coefficients[1])),3)
      decayrt4[[2,i]] = signif(-as.numeric(saved.fits4[[i]]$coefficients[2]),3)
      decayrt4[[3,i]] = signif(exp(as.numeric(saved.fits4[[i]]$coefficients[3])),3)
      decayrt4[[4,i]] = signif(-as.numeric(saved.fits4[[i]]$coefficients[4]),3)
      decayrt4[[5,i]] = signif(exp(as.numeric(saved.fits4[[i]]$coefficients[5])),3)
      decayrt4[[6,i]] = signif(-as.numeric(saved.fits4[[i]]$coefficients[6]),3)
    }
  }
  
  fits4allpara = cbind(fits4aic,t(decayrt4))
  fits4allpara = as.data.frame(fits4allpara)
  colnames(fits4allpara) = c("AIC","RU1","kd1","RU2","kd2","RU3","kd3")
  fits4allpara = fits4allpara[order(fits4allpara$AIC),]
 
  comp3fits[[j]] = saved.fits4[[as.numeric(rownames(fits4allpara)[1])]]
  comp3temp = as.numeric(fits4allpara[1,])
  comp3temp2 = as.data.frame(split(comp3temp[-1], rep(1:2)))
  comp3sdtemp = signif(deltamethod(c(~exp(x1),~-x2,~exp(x3),~-x4,~exp(x5),~-x6), coefficients(comp3fits[[j]]), vcov(comp3fits[[j]])),3)
  comp3sdtemp2 = as.data.frame(split(comp3sdtemp, rep(1:2)))
  comp3sdtemp3 = cbind(comp3temp2,comp3sdtemp2)
  comp3temp3 = comp3sdtemp3[order(abs(comp3sdtemp3[,2]), decreasing = F),]
  comp3temp4 = as.numeric(unlist(t(comp3temp3)))
  comp3temp5 = c(comp3temp[1],comp3temp4)
  comp3fitstat[j,] = comp3temp5
  comp3fitpass[j] = "Y"
  }
  
  # Record results for 1 component fit

  
  if(length(saved.fits5)==0)
  {
    comp1fits[[j]] = y
    comp1fitstat[j,] = c(0,0,0.0000001,0,0)
    fits5allpara = as.data.frame(t(rbind(rep(0,100),rep(0,100),rep(0.0000001,100))))
    colnames(fits5allpara) = c("AIC","RU1","kd1")
    comp1fitpass[j] = "N"
  }
  else
  {
  for (i in 1:100)
  {
    if(capture.output(saved.fits5[[i]]) == "NULL"){fits5aic[i]  = 0}else{fits5aic[i] = AIC(saved.fits5[[i]])[1]}
  }
  
  decayrt5 = array(NA,dim = c(2,100))
  for (i in 1:100)
  {
    if(capture.output(saved.fits5[[i]]) != "NULL")
    {
      decayrt5[[1,i]] = signif(exp(as.numeric(saved.fits5[[i]]$coefficients[1])),3)
      decayrt5[[2,i]] = signif(-as.numeric(saved.fits5[[i]]$coefficients[2]),3)
    }
  }
  
  fits5allpara = cbind(fits5aic,t(decayrt5))
  fits5allpara = as.data.frame(fits5allpara)
  colnames(fits5allpara) = c("AIC","RU1","kd1")
  fits5allpara = fits5allpara[order(fits5allpara$AIC),]
  
  comp1fits[[j]] = saved.fits5[[as.numeric(rownames(fits5allpara)[1])]]
  comp1sdtemp = signif(deltamethod(c(~exp(x1),~-x2), coefficients(comp1fits[[j]]), vcov(comp1fits[[j]])),3)
  comp1fitstat[j,] = c(as.numeric(fits5allpara[1,]),comp1sdtemp)
  comp1fitpass[j] = "Y"
  }
  }
  
  print(j)
}
```

Export fit report
```{r}
pdf("PAART fit - plots.pdf", width = 10, height = 9)
for (j in normallist)
{
par(mfrow=c(4,3))
plot(rawfull[[j]], xlab = "Time (s)", ylab = "Response (nm)")
abline(v = plotstart)
abline(v = as.numeric(uniquesample$Start[j]), col = "red")
abline(v = as.numeric(uniquesample$Stop[j]), col = "red")
title("Original Data", adj = 0.5, line = 0.5)
plot(rawpointplot[[j]], ylim=c(0, max(rawpoint[[j]][,2])), xlab = "Time (s)", ylab = "Response (nm)", col = "gray50")
lines(rawpoint[[j]][,1],if(comp2fitpass[j]=="N"){rep(0,length(rawpoint[[j]][,1]))}else{fitted(comp2fits[[j]])}, col = "red")
lines(rawpoint[[j]][,1],comp2fitstat[j,2]*exp(-comp2fitstat[j,3]*rawpoint[[j]][,1]), col = "blue")
lines(rawpoint[[j]][,1],comp2fitstat[j,6]*exp(-comp2fitstat[j,7]*rawpoint[[j]][,1]), col = "orange")
title("2 components", adj = 0.5, line = 0.5)
plot(rawpointplot[[j]], ylim=c(0, max(rawpoint[[j]][,2])), xlab = "Time (s)", ylab = "Response (nm)", col = "gray50")
lines(rawpoint[[j]][,1],if(comp3fitpass[j]=="N"){rep(0,length(rawpoint[[j]][,1]))}else{fitted(comp3fits[[j]])}, col = "red")
lines(rawpoint[[j]][,1],comp3fitstat[j,2]*exp(-comp3fitstat[j,3]*rawpoint[[j]][,1]), col = "blue")
lines(rawpoint[[j]][,1],comp3fitstat[j,6]*exp(-comp3fitstat[j,7]*rawpoint[[j]][,1]), col = "orange")
lines(rawpoint[[j]][,1],comp3fitstat[j,10]*exp(-comp3fitstat[j,11]*rawpoint[[j]][,1]), col = "purple")
title("3 components", adj = 0.5, line = 0.5)
plot(rawpointplot[[j]], xlab = "Time (s)", ylab = "Response (nm)", col = "gray50")
lines(rawpoint[[j]][,1],if(comp1fitpass[j]=="N"){rep(0,length(rawpoint[[j]][,1]))}else{fitted(comp1fits[[j]])}, col = "red")
title("1 component (fit conly)", adj = 0.5, line = 0.5)
plot(rawpointplot[[j]], xlab = "Time (s)", ylab = "Response (nm)", col = "gray50")
lines(rawpoint[[j]][,1],if(comp2fitpass[j]=="N"){rep(0,length(rawpoint[[j]][,1]))}else{fitted(comp2fits[[j]])}, col = "red")
title("2 components (fit conly)", adj = 0.5, line = 0.5)
plot(rawpointplot[[j]], xlab = "Time (s)", ylab = "Response (nm)", col = "gray50")
lines(rawpoint[[j]][,1],if(comp3fitpass[j]=="N"){rep(0,length(rawpoint[[j]][,1]))}else{fitted(comp3fits[[j]])}, col = "red")
title("3 components (fit conly)", adj = 0.5, line = 0.5)
plot(rawpoint[[j]][,1], if(comp1fitpass[j]=="N"){rep(0,length(rawpoint[[j]][,1]))}else{rawpoint[[j]][,2]-fitted(comp1fits[[j]])}, xlim = c(0, plotend-as.numeric(uniquesample$Start[j])), xlab = "Time (s)", ylab = "Response (nm)")
abline(h = 0)
title("1 component (residual)", adj = 0.5, line = 0.5)
plot(rawpoint[[j]][,1], if(comp2fitpass[j]=="N"){rep(0,length(rawpoint[[j]][,1]))}else{rawpoint[[j]][,2]-fitted(comp2fits[[j]])}, xlim = c(0, plotend-as.numeric(uniquesample$Start[j])), xlab = "Time (s)", ylab = "Response (nm)")
abline(h = 0)
title("2 components (residual)", adj = 0.5, line = 0.5)
plot(rawpoint[[j]][,1], if(comp3fitpass[j]=="N"){rep(0,length(rawpoint[[j]][,1]))}else{rawpoint[[j]][,2]-fitted(comp3fits[[j]])}, xlim = c(0, plotend-as.numeric(uniquesample$Start[j])), xlab = "Time (s)", ylab = "Response (nm)")
abline(h = 0)
title("3 components (residual)", adj = 0.5, line = 0.5)
plot.new()
vps1 = baseViewports()
plot.new()
vps2 = baseViewports()
plot.new()
vps3 = baseViewports()
pushViewport(vps1$inner, vps1$figure, vps1$plot)
comp1tabletemp = as.data.frame(rbind(c(comp1fitstat[j,2],comp1fitstat[j,4],formatC(comp1fitstat[j,3], format = "e", digits = 2),formatC(comp1fitstat[j,5], format = "e", digits = 2)),c("","","",""),c("","","",""),c(formatC(comp1fitstat[j,1], format = "f", digits = 2),"","","")))
colnames(comp1tabletemp) = c("Response","Std","Off rate","Std")
rownames(comp1tabletemp) = c("#1","",".","AIC")
grid.table(comp1tabletemp,theme=ttheme_minimal(base_size = 8))
popViewport(3)
pushViewport(vps2$inner, vps2$figure, vps2$plot)
comp2tabletemp = as.data.frame(rbind(c(comp2fitstat[j,2],comp2fitstat[j,4],formatC(comp2fitstat[j,3], format = "e", digits = 2),formatC(comp2fitstat[j,5], format = "e", digits = 2)),c(comp2fitstat[j,6],comp2fitstat[j,8],formatC(comp2fitstat[j,7], format = "e", digits = 2),formatC(comp2fitstat[j,9], format = "e", digits = 2)),c("","","",""),c(formatC(comp2fitstat[j,1], format = "f", digits = 2),"","","")))
colnames(comp2tabletemp) = c("Response","Std","Off rate","Std")
rownames(comp2tabletemp) = c("#1","#2","","AIC")
grid.table(comp2tabletemp,theme=ttheme_minimal(base_size = 8))
popViewport(3)
pushViewport(vps3$inner, vps3$figure, vps3$plot)
comp3tabletemp = as.data.frame(rbind(c(comp3fitstat[j,2],comp3fitstat[j,4],formatC(comp3fitstat[j,3], format = "e", digits = 2),formatC(comp3fitstat[j,5], format = "e", digits = 2)),c(comp3fitstat[j,6],comp3fitstat[j,8],formatC(comp3fitstat[j,7], format = "e", digits = 2),formatC(comp3fitstat[j,9], format = "e", digits = 2)),c(comp3fitstat[j,10],comp3fitstat[j,12],formatC(comp3fitstat[j,11], format = "e", digits = 2),formatC(comp3fitstat[j,13], format = "e", digits = 2)),c(formatC(comp3fitstat[j,1], format = "f", digits = 2),"","","")))
colnames(comp3tabletemp) = c("Response","Std","Off rate","Std")
rownames(comp3tabletemp) = c("#1","#2","#3","AIC")
grid.table(comp3tabletemp,theme=ttheme_minimal(base_size = 8))
popViewport(3)
mtext(pagetitles[j], side = 3, line = -2, outer = TRUE)
}
dev.off()
```

Export stats report

```{r}
comp1fitstat1 = as.data.frame(comp1fitstat)
comp2fitstat1 = as.data.frame(comp2fitstat[,c(1,2,3,6,7,4,5,8,9)])
comp3fitstat1 = as.data.frame(comp3fitstat[,c(1,2,3,6,7,10,11,4,5,8,9,12,13)])
colnames(comp1fitstat1) = c("AIC","Response1","kd1","RespSD1","kdSD1")
colnames(comp2fitstat1) = c("AIC","Response1","kd1","Response2","kd2","RespSD1","kdSD1","RespSD2","kdSD2")
colnames(comp3fitstat1) = c("AIC","Response1","kd1","Response2","kd2","Response3","kd3","RespSD1","kdSD1","RespSD2","kdSD2","RespSD3","kdSD3")
write.xlsx(comp1fitstat1, file = "PAART fit - stats.xlsx", sheetName="1 component", append=FALSE)
write.xlsx(comp2fitstat1, file = "PAART fit - stats.xlsx", sheetName="2 components", append=TRUE)
write.xlsx(comp3fitstat1, file = "PAART fit - stats.xlsx", sheetName="3 components", append=TRUE)
```